WHOOMP! (There It Is) \\ Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2014-08-11 ms.tex
Fix typo

In this paper we present a rapid and accurate method of sky localization that makes use of Bayesian methods. It differs from existing techniques in several important ways.  In the first place, we fix the intrinsic parameters to their \ac{ML} estimates, as provided by the detection pipeline.  This reduces the dimensionality of the parameter space we need to sample. In addition, the technique takes as its input the \ac{ML} estimates of the extrinsic parameters, instead of the $h(t)$ time series. This makes the likelihood itself much faster to evaluate. Finally, instead of of using \ac{MCMC} or some similar method for statistical sampling, we make use of a deterministic quadrature scheme. We call this technique \ac{BAYESTAR}%
%
\footnote{A pun on the Cylon battleships in the American television series Battlestar Galactica. The defining characteristic of the Cylons is that they repeatedly defeat humanity by using their superhuman information\nobreakdashes-gathering ability to coordinate overwhelming forces. The name also suggests that, like the Cylons, \ac{GW} detectors may some day rise against us humans.}%
%
\footnote{We do not like to mention the final `L' in the acronym, because then it would be pronounced BAYESTARL, which sounds stupid.}%
. It is unique in that in bridges the detection and parameter estimation of \ac{GW} signals, two tasks that have until now involved very different numerical methods and time scales. We expect that \ac{BAYESTAR} will take on a key role in observing \ac{CBC} events in both \ac{GW} and optical channels during the Advanced \ac{LIGO} era.

@@

The distance prior is a user-selected power of distance,
%
\begin{equation*}
    p(r) \propto \cases{
        r^m & if $r_\mathrm{min} < r < r_\mathrm{max}$ \\
        0 & otherwise
    }
\end{equation*}
%
where $m=2$ for a prior that is uniform in volume, and $m=-1$. If a distance prior is not specified, the default is uniform in volume out to the maximum SNR=4 horizon distance:
%
\begin{equation*}
    m = 2,
    \qquad
    r_\mathrm{min} = 0,
    \qquad
    r_\mathrm{max} = \frac{1}{4} \max_i r_{1,i}.
\end{equation*}

>>>>

In this paper we present a rapid and accurate method of sky localization that makes use of Bayesian methods. It differs from existing techniques in several important ways.  In the first place, we fix the intrinsic parameters to their \ac{ML} estimates, as provided by the detection pipeline.  This reduces the dimensionality of the parameter space we need to sample. In addition, the technique takes as its input the \ac{ML} estimates of the extrinsic parameters, instead of the $h(t)$ time series. This makes the likelihood itself much faster to evaluate. Finally, instead of of using \ac{MCMC} or some similar method for statistical sampling, we make use of a deterministic quadrature scheme. We call this technique \ac{BAYESTAR}%
%
\footnote{A pun on the Cylon battleships in the American television series Battlestar Galactica. The defining characteristic of the Cylons is that they repeatedly defeat humanity by using their superhuman information\nobreakdashes-gathering ability to coordinate overwhelming forces. The name also suggests that, like the Cylons, \ac{GW} detectors may some day rise against us humans.}%
%
\footnote{We do not like to mention the final `L' in the acronym, because then it would be pronounced BAYESTARL, which sounds stupid.}%
. It is unique in that it bridges the detection and parameter estimation of \ac{GW} signals, two tasks that have until now involved very different numerical methods and time scales. We expect that \ac{BAYESTAR} will take on a key role in observing \ac{CBC} events in both \ac{GW} and optical channels during the Advanced \ac{LIGO} era.

@@

The distance prior is a user-selected power of distance,
%
\begin{equation*}
    p(r) \propto \cases{
        r^m & if $r_\mathrm{min} < r < r_\mathrm{max}$ \\
        0 & otherwise
    }
\end{equation*}
%
where $m=2$ for a prior that is uniform in volume, and $m=-1$ for a prior that is uniform in the logarithm of the distance. If a distance prior is not specified, the default is uniform in volume out to the maximum SNR=4 horizon distance:
%
\begin{equation*}
    m = 2,
    \qquad
    r_\mathrm{min} = 0,
    \qquad
    r_\mathrm{max} = \frac{1}{4} \max_i r_{1,i}.
\end{equation*}
